\documentstyle [12pt]{article}
\oddsidemargin=0in
\evensidemargin=0in
\setlength{\textwidth}{6.5in}
\topmargin=-0.25in
\setlength{\textheight}{8.5in}
\pagestyle{plain}

\pagenumbering{arabic}

\newtheorem{art}{Article}
\newtheorem{sect}{Section}[art]

\begin{document}
\bigskip

\title{Constitution of the Linux Users Group at North Carolina State University} 
\author{}
\date{21 November 2000}
\maketitle

\bigskip
\bigskip

\begin{art} {\bf Name and Purpose}
\label{art-name}

\begin{sect}
This organization shall be known as the Linux Users Group (LUG) at North Carolina State University.
\end{sect}

\begin{sect}
The purpose of this organization is to promote the use and usability of Linux
in the NCSU community.  This includes such activities such as informational talks, installfests, and open forums.
\end{sect}

\end{art}

\bigskip
\begin{art} {\bf Membership}
\label{art-memb}

\begin{sect}
Membership shall be open to all regularly enrolled students, staff, or faculty of NCSU who are interested in Linux.  Members may be elected to office.
\end{sect}

\begin{sect}
People in the surrounding community that are not a student, faculty,
or staff member of NCSU may be ``associate members''.  Per NCSU administrative regulations, they may not hold office in LUG.
\end{sect}

\end{art}

\bigskip
\begin{art} {\bf Officers}
\label{art-off}

\begin{sect}
The officers of this organization shall be:
\begin{description}
\item[\hspace*{0.25in} President:]
Responsible for leading the Steering Committee, directing 
the meetings, and assigning additional duties as necessary.
\item[\hspace*{0.25in} Vice-President:]
Assists the president as necessary and fills in for the President when
absent.
\item[\hspace*{0.25in} Treasurer:]
Responsible for maintaining an accounting of all LUG funds.
\item[\hspace*{0.25in} Secretary:]
Responsible for preparing the official minutes of each meeting and
for e-mailing meeting announcements for meetings and other events.
\item[\hspace*{0.25in} Webmaster:]
Responsible for maintaining the website.
\end{description}
All of the Officers and any Chairpersons (See Article~\ref{art-coms}) will make up the Steering Committee which is responsible for the operation of the LUG.
Meetings shall be directed by the President or any other member of the Steering Committee.  In the event that the President is absent, meetings shall be directed by the Vice-President, then the Secretary, then the Treasurer, then any other member of the Steering Committee, in that order.

\end{sect}

\begin{sect}
Elections shall be held at the last meeting of the semester before the
start of exams (as published by Registration and Records).  There must be
at least 5 members in attendance excepting the candidates to hold an election.
Elections may also be held in the case of a vacancy or at the discretion of the
Steering Committee at a regularly scheduled meeting provided that an
announcement has been made at least one week prior to the election.
\end{sect}
\begin{sect}
The officers shall be elected by the organization members to serve a term of one
semester.  A officer shall continue to hold their office in future semesters
if 1) they remain affiliated with NCSU as either a student, staff, or faculty
member; 2) The officer does not get elected
into another officer position in the LUG; 3) The officer does not object
to serving another semester.
\end{sect}
\begin{sect}
The membership at large may remove an officer by a two-thirds (2/3) majority at 1) an election meeting, or 2) any other meeting provided that it is announced at least 1 week in advance that a motion will be made to remove an officer.
\end{sect}
\begin{sect}
Members and associate members in attendance at an election meeting are eligible to vote in an election.
\end{sect}

\end{art}

\bigskip
\begin{art} {\bf Dues}
\label{art-dues}

\begin{sect}
There are no fixed dues for the LUG.
\end{sect}

\begin{sect}
If deemed necessary the Steering Committee can request a special assessment
from the organization members.  This request must be approved by the majority of
the organization members present and voting at a regularly scheduled meeting.
\end{sect}

\begin{sect}
Disbursement of funds is at the discretion of the Steering Committee.
\end{sect}

\end{art}

\bigskip
\begin{art} {\bf Amending the Constitution}
\label{art-amemd}

\begin{sect}
Amendments to the constitution shall be presented by members of the
organization in writing at a regular meeting but shall not be voted
upon until the next regular meeting, and then only after informing
each member of the proposed amendments.  A majority of 2/3 of the
members present and voting shall be required.
\end{sect}

\end{art}

\bigskip
\bigskip
\begin{art} {\bf Meetings}
\label{art-meet}

\begin{sect}
The LUG shall hold meetings at least once every two weeks.
More frequent meetings can be scheduled at the discretion of the 
Steering Committee.
\end{sect}
\begin{sect}
The time, date, and location of meetings shall be distributed to
members during the first two weeks of a semester by a member of the
steering committee at a meeting and other means such as e-mailing the LUG
mailing list or the LUG web page.
\end{sect}
\begin{sect}
At the discretion of the steering committee, a meeting can be canceled
due to events such as, but not limited to, student semester exams, university
holidays, student breaks, and adverse weather.
\end{sect}
\begin{sect}
Official LUG business will be handled at meetings and any actions will be
decided by a consensus of the members present.
\end{sect}

\end{art}

\bigskip
\begin{art} {\bf Committees}
\label{art-coms}

\begin{sect}
The Steering Committee can form committees for special projects or
assignments as necessary. The members of the committees are to be drawn
from the current members on a volunteer basis.
\end{sect}

\begin{sect}
At least one member of the committee will be designated as the Chairperson of
the Committee.  All Chairpersons will be members of the Steering Committee
(See Article~\ref{art-off}).
\end{sect}

\end{art}

\vfil
\end{document}

